%-------------------------
% Resume in Overleaf LaTeX
% Author : Joseph (Joe) Lollo
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Joseph (Joe) Lollo, MLIS} \\ \vspace{1pt}
    \small 425-623-5253 $|$ \href{mailto:joelollo880@gmail.com}{\underline{joelollo880@gmail.com}} $|$ 
    \href{https://linkedin.com/in/joelollo21}{\underline{linkedin.com/in/joelollo21}} $|$
    \href{https://sites.google.com/view/joe-lollo-mlis}{\underline{sites.google.com/joe-lollo-mlis}}
\end{center}


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Interpersonal Skills}{: Community Engagement and Outreach, User Research, Curriculum Development, Project Management, Library Reference, Customer Service, Cultural Humility, Event Planning, Social Media.} \\
     \textbf{Technical Skills}{: Microsoft Office, Adobe Creative Suite, Canvas, Camtasia, WordPress, Ex Libris Alma, Omeka, HTML, CSS, JavaScript, Canva, Figma.} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Master of Library and Information Science}{2024}
    \resumeSubheading
      {University of Washington Bothell}{Bothell, WA}
      {Bachelor of Arts in English Literature and Media Studies}{2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Contract Research and Instruction Librarian}{Sep. -- Dec. 2024}
      {Seattle University}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Provided research assistance to students, faculty, and staff at the Research Help desk and in online consultations.}
        \resumeItem{Taught database and web searching to 9 undergraduate classes, with individualized lesson plans and assessments.}
        \resumeItem{Designed posters and fliers promoting library services, using Adobe Illustrator and Photoshop.}
        \resumeItem{Created and edited video tutorials with Camtasia, sharing library resources and research tools with the public.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Graduate Student Specialist, Libraries Instructional Design (LibID)}{Aug. 2022 -- Aug. 2024}
      {University of Washington Libraries}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Collaborate on the design and facilitation of 10+ library outreach workshops, introducing digital technologies and library resources to the campus community.}
        \resumeItem{Developed engaging digital content for the LibID team's Canvas and WordPress pages, including blogs, video tutorials, and infographics.}
        \resumeItem{Provided 1-on-1 mentorship to workshop participants to meet personal and professional goals.}
        \resumeItem{Created and taught original workshop on \emph{Web Design with WordPress} to 22 students in Winter quarter 2024.}
    \resumeItemListEnd

    \resumeSubheading
      {Capstone Design Intern, \emph{The Misinformation Play Pack}}{Dec. 2023 -- May 2024}
      {University of Washington, Game Research Group}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Collaborated on the design of an online curriculum for public libraries and K-12 educators to teach about misinformation and digital equity.}
        \resumeItem{Developed 50+ digital learning artifacts, including lesson plans, activity printouts, PowerPoint slides, and videos.}
        \resumeItem{Partnered with the Seattle Public Library to conduct research with 10 teen users, collecting feedback on curriculum strengths and areas of improvement.}
        \resumeItem{Researched game-based learning to enhance curriculum flexibility and develop 8-page framing document.}
      \resumeItemListEnd

    \resumeSubheading
      {Peer Academic Advisor}{June 2021 -- Aug. 2022}
      {University of Washington Bothell}{Bothell, WA}
      \resumeItemListStart
        \resumeItem{Counseled 200+ undergraduate students on majors, classes, and study habits from a peer-to-peer perspective.}
        \resumeItem{Coordinated 3 outreach events introducing first-year and transfer students to campus resources.}
        \resumeItem{Conducted presentations on academic planning at 5 New Student Orientations, improving new students' familiarity with university policies and requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\emph{Baloney Detectives}} $|$ \emph{UX Designer, UW class project}}{Jan. -- March 2023}
          \resumeItemListStart
            \resumeItem{Designed interactive game mimicking the psychological effects on health misinformation and social media, on a cross-functional team of 4.}
            \resumeItem{Interviewed 5 direct stakeholders to solicit feedback on learning outcomes and desired game features.}
            \resumeItem{Used Twine (HTML/CSS), and itch.io to develop high-fidelity prototype using stakeholder feedback.}
            \resumeItem{Facilitated learning experience using the game for 30+ high school students at UW's Misinfo Day conference.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%


%-------------------------------------------
\end{document}
